Optimal (Multiway) Spatial Joins

### 2024-06-01 5-comp.tex
5-comp

W.l.o.g., we assume that each segment in the input $H$ is given a distinct integer ID in $[|H|]$. This allows us to create an array of size $|H|$ and allocate an array cell to each $h \in H$, with the property that the cell can be accessed by the ID of $h$ in constant time.

>>>>

W.l.o.g., we assume that each segment in the input $H$ is given a distinct integer ID in $[|H|]$. This allows us to create an array of size $|H| < n$ and allocate an array cell to each $h \in H$, with the property that the cell can be accessed by the ID of $h$ in constant time.
